---
title: "Customizing Branding"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Customizing Branding}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`typstR` exposes branding through YAML fields in `template.qmd`. The intended
workflow is to edit those fields in Quarto, not to patch the shipped Typst
template.

## Start from the commented branding block

The working paper starter ships with these commented fields:

```yaml
typstR:
  # logo: "logo.png"
  # accent-color: "#0A5DA6"
  # primary-font: "Linux Libertine"
  # footer: "Working Paper Series"
  # disclaimer-page: true
```

Uncomment the fields you need and keep the rest at their defaults.

## Add a logo and accent color

Use `logo` for an image path relative to the manuscript, and `accent-color`
for the main highlight color used by the format.

```yaml
typstR:
  logo: "logo.png"
  accent-color: "#0A5DA6"
```

This is usually enough to align the title page with an institute or working
paper series.

## Change the primary font and footer

`primary-font` changes the main text family, while `footer` adds short text to
the page footer.

```yaml
typstR:
  primary-font: "Linux Libertine"
  footer: "Working Paper Series"
```

Use a font that is available in the rendering environment. If you are sharing a
project, document any non-default font requirement alongside the manuscript.

## Adjust margins and disclaimer behavior

You can also set custom margins and enable a disclaimer page directly in YAML.

```yaml
typstR:
  margins:
    x: 1.1in
    y: 1in
  disclaimer-page: true
```

`disclaimer-page` is useful when a series needs a standard notice ahead of the
main manuscript.

## Render only when Quarto is available

Branding changes take effect at render time, so the example call stays
non-evaluated in the vignette:

```{r eval = FALSE}
render_working_paper("my-paper/template.qmd")
```

If the output does not look right, inspect the YAML field names first. The most
common mistake is using a near miss such as `accent_color` instead of
`accent-color`.
