---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`typstR` is built around one fast path: scaffold a working paper, edit one
Quarto file, and render a PDF when Quarto is available.

## Create a project

Start by creating a working paper directory:

```{r}
library(typstR)
```

```{r eval = FALSE}
create_working_paper("my-paper")
```

This creates a small project with:

- `template.qmd` for the manuscript
- `_quarto.yml` for project settings
- `references.bib` for bibliography entries
- the bundled `typstR` extension used by the template

## Edit `template.qmd`

The working-paper template already contains the main fields most users need:
title, authors, affiliations, an abstract, bibliography wiring, and a
`typstR:` block for publication metadata.

```yaml
typstR:
  keywords:
    - supply chains
    - trade policy
  jel:
    - F14
    - F13
  report-number: "WP 001"
  funding: |
    This research was supported by the Applied Trade Policy Programme.
```

You can also build structured metadata in R before pasting it into the Quarto
file:

```{r}
lead_author <- author(
  "Elena Fischer",
  email = "elena.fischer@example.org",
  corresponding = TRUE,
  affiliation = "1"
)

home_institute <- affiliation("1", "Centre for European Industrial Analysis")

manuscript_meta(
  authors = list(lead_author),
  affiliations = list(home_institute)
)
```

## Add manuscript content

Keep the manuscript in `template.qmd`. The shipped starter uses a compact
working-paper structure:

- `Introduction`
- `Data and Methods`
- `Results`
- `Conclusion`
- `References`

Add citations through `references.bib` and cite them in the manuscript with
standard Quarto syntax such as `@smith2020`.

## Render the PDF

Rendering depends on Quarto, so the call below is shown but not run during
vignette checks.

```{r eval = FALSE}
render_working_paper("my-paper/template.qmd")
```

If you prefer to guard the call in your own scripts, use the same condition
that package tests use:

```{r}
quarto_ready <- quarto::quarto_available()
quarto_ready
```

```{r eval = FALSE}
if (quarto::quarto_available()) {
  render_working_paper("my-paper/template.qmd")
}
```

## Next steps

Once the basic workflow is working, the other vignettes cover the two main
follow-up tasks:

- `vignette("working-papers", package = "typstR")` for working-paper metadata
- `vignette("customizing-branding", package = "typstR")` for branding fields
